Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-05-16 ms.tex
Update on Overleaf.

% \begin{figure}
% \includegraphics[width=\linewidth]{figures/multidim_parameter_space.pdf}
% % \includegraphics[width=\linewidth]{fig_01.pdf}
% \caption{
% \label{fig:multidim-parameter-space}}
% \end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/multidim_beamformer_dft_cost_analysis_SKA1-low.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:multidim-incoherent-compcost-BF-SKA-low}}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{figures/1D_beamformer_dft_cost_analysis_SKA1-low.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-BF-SKA-low}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-EPIC-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_epic_cost_analysis_SKA1-low.pdf}}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-EPIC-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_epic_relative_cost_analysis_SKA1-low.pdf}}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using station-level EPIC for \texttt{SKA-low}. Cyan contours  \label{fig:incoherent-compcost-EPIC-SKA-low}}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{figures/1D_epic_cost_analysis_SKA1-low.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-EPIC-SKA-low}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-XBF-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_xcor_dft_cost_analysis_SKA1-low.pdf}}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-XBF-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_xcor_dft_relative_cost_analysis_SKA1-low.pdf}}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{SKA-low-core}, \texttt{SKA-low}, \texttt{Aus-VLBA-low}, and \texttt{IC-VLBA-low}. Cyan contours  \label{fig:incoherent-compcost-XBF-SKA-low}}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{figures/1D_xcor_dft_cost_analysis_SKA1-low.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-XBF-SKA-low}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-XFFT-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_xcor_fft_cost_analysis_SKA1-low.pdf}}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-XFFT-SKA-low}]{\includegraphics[width=0.48\textwidth]{figures/multidim_xcor_fft_relative_cost_analysis_SKA1-low.pdf}}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using an FFT of station-level cross-correlations for \texttt{SKA-low-core}, \texttt{SKA-low}, \texttt{Aus-VLBA-low}, and \texttt{IC-VLBA-low}. Cyan contours  \label{fig:incoherent-compcost-XFFT-SKA-low}}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{figures/1D_xcor_fft_cost_analysis_SKA1-low.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-XFFT-SKA-low}}
\end{figure}

\begin{figure}
\centering
\subfloat[][One-dimensional slices \label{fig:1D-incoherent-compcost-SKA-low}]{\includegraphics[width=\textwidth]{figures/1D_compcost_analysis_SKA1-low.pdf}} \\
\subfloat[][One-dimensional slices (relative)\label{fig:1D-incoherent-compcost-XFFT-IC-VLBA-low}]{\includegraphics[width=\textwidth]{figures/1D_relative_compcost_analysis_SKA1-low.pdf}}
\caption{(Left): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, \texttt{Aus-VLBA-low}, and \texttt{IC-VLBA-low}. Cyan contours  \label{fig:1D-incoherent-compcost-SKA-low}}
\end{figure}

@@

@@

\begin{figure*}
\includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_SKA1-low-core.pdf} 
\caption{Computational cost of coherent strategy for \texttt{SKA-low-core} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-SKA-low-core}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_SKA1-low.pdf}
\caption{Computational cost of coherent strategy for \texttt{SKA-low} relative to BF+XFFT strategy.  \label{fig:1D-coherent-relative-compcost-SKA-low}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_AU-VLBA-low.pdf}
\caption{Computational cost of coherent strategy for \texttt{Aus-VLBA-low} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-Aus-VLBA-low}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_IC-VLBA-low.pdf}
\caption{Computational cost of coherent strategy for \texttt{IC-VLBA-low} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-IC-VLBA-low}}
\end{figure*}

>>>>

% \begin{figure}
% \includegraphics[width=\linewidth]
% {figures/multidim_parameter_space.pdf}
% \caption{
% \label{fig:multidim-parameter-space}}
% \end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_beamformer_dft_cost_analysis_SKA1-low.pdf}
{figures/1D_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A breakdown of the computational cost density function over the instrument parameters for \texttt{LAMBDA-I} using the voltage beamforming architecture at the station level.
\label{fig:1D-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/multidim_beamformer_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_beamformer_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{A multi-dimensional view of the net computational cost density function over the instrumental parameters for \texttt{LAMBDA-I} using the voltage beamforming architecture at the station level.
\label{fig:multidim-incoherent-compcost-BF-LAMBDA-I}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_epic_cost_analysis_SKA1-low.pdf}
{figures/1D_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure}

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-EPIC-LAMBDA-I}]{\includegraphics[width=0.48\textwidth]
% {figures/multidim_epic_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_epic_relative_cost_analysis_LAMBDA-I.pdf}
} 
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using station-level EPIC for \texttt{SKA-low}. Cyan contours  \label{fig:incoherent-compcost-EPIC-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/1D_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
% \includegraphics[width=\linewidth]{fig_01.pdf}
\caption{
\label{fig:1D-incoherent-compcost-XBF-LAMBDA-I}}
\end{figure}

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-XBF-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_dft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_dft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using a DFT of station-level cross-correlations for \texttt{SKA-low-core}, \texttt{SKA-low}, \texttt{Aus-VLBA-low}, and \texttt{IC-VLBA-low}. Cyan contours  \label{fig:incoherent-compcost-XBF-LAMBDA-I}}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=\linewidth]
% {figures/1D_xcor_fft_cost_analysis_SKA1-low.pdf}
{figures/1D_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
\caption{
\label{fig:1D-incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure}

\begin{figure*}
\centering
\subfloat[][Two-dimensional slices \label{fig:multidim-incoherent-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_fft_per_pixel_cost_analysis_LAMBDA-I.pdf}
}
\subfloat[][Two-dimensional slices (relative)\label{fig:multidim-incoherent-relative-compcost-XFFT-LAMBDA-I}]
{\includegraphics[width=0.48\textwidth]
% {figures/multidim_xcor_fft_relative_cost_analysis_SKA1-low.pdf}
{figures/multidim_xcor_fft_relative_cost_analysis_LAMBDA-I.pdf}
}
\caption{(Left): Two-dimensional slices of the computational cost for coherent-incoherent imaging using an FFT of station-level cross-correlations for . Cyan contours  \label{fig:incoherent-compcost-XFFT-LAMBDA-I}}
\end{figure*}

\begin{figure}
\centering
\subfloat[][One-dimensional slices \label{fig:1D-incoherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
% {figures/1D_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][One-dimensional slices (relative)\label{fig:1D-incoherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
% {figures/1D_relative_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][One-dimensional slices (relative)\label{fig:1D-incoherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
% {figures/1D_relative_compcost_analysis_SKA1-low.pdf}
{figures/1D_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{(Top): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}. (Middle): Same for \texttt{CASPA}. (Bottom): Same for \texttt{FarView}. \label{fig:1D-incoherent-compcost}}
\end{figure}

@@

\begin{figure*}
\centering
\subfloat[][\texttt{LAMBDA-I} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][\texttt{SKA1-Low-core} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low-core.pdf}
} \\
\subfloat[][\texttt{SKA1-Low} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low.pdf}
} 
\caption{(Top): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}. (Middle): Same for \texttt{CASPA}. (Bottom): Same for \texttt{FarView}. \label{fig:1D-incoherent-compcost-a}}
\end{figure*}

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. (Top): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}. (Middle): Same for \texttt{CASPA}. (Bottom): Same for \texttt{FarView}. \label{fig:1D-incoherent-compcost}}
\end{figure*}

@@

% \begin{figure*}
% \includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_SKA1-low-core.pdf} 
% \caption{Computational cost of coherent strategy for \texttt{SKA-low-core} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-SKA-low-core}}
% \end{figure*}

% \begin{figure*}
% \includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_SKA1-low.pdf}
% \caption{Computational cost of coherent strategy for \texttt{SKA-low} relative to BF+XFFT strategy.  \label{fig:1D-coherent-relative-compcost-SKA-low}}
% \end{figure*}

% \begin{figure*}
% \includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_AU-VLBA-low.pdf}
% \caption{Computational cost of coherent strategy for \texttt{Aus-VLBA-low} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-Aus-VLBA-low}}
% \end{figure*}

% \begin{figure*}
% \includegraphics[width=0.95\textwidth]{figures/1D_coherent_relative_compcost_analysis_IC-VLBA-low.pdf}
% \caption{Computational cost of coherent strategy for \texttt{IC-VLBA-low} relative to BF+XFFT strategy. \label{fig:1D-coherent-relative-compcost-IC-VLBA-low}}
% \end{figure*}
